Defining Greatness

### 2024-11-26 paper/paper.qmd
Final touches, tidy folders up

---
title: "Defining Greatness"
subtitle: "A Comparative Analysis of Tom Brady and Patrick Mahomes"
author: 
  - Alexander Guarasci
thanks: "Code and data are available at: https://github.com/AlexanderG123/nfl"
date: today
date-format: long
abstract: "This paper compares NFL quarterbacks Tom Brady and Patrick Mahomes, focusing on their statistical performances. Analyzing their respective career data, this paper uses predictive modelling to forecast Patrick Mahomes future. It finds that while both have impressive career statistics, ultimately, playoff victories, particularly Super Bowl wins, serve as a more definitive measure of greatness. By examining these players, the paper highlights how the NFL’s dynamic context impacts player evaluation and legacy assessment."
format: 
  pdf: 
    fig-pos: "H"
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

The analysis was conducted in R [@citeR], leveraging tools from the Tidyverse [@citetidyverse], Arrow [@citearrow], Knitr [@citeknitr] packages. The primary dataset included QB-specific data from every NFL game played since 2000, encompassing over 55 columns detailing various player performance metrics. Additional data sources were used for advanced metrics, notably ESPN’s Quarterback Rating (QBR), which encapsulates QB efficiency across multiple dimensions of gameplay.

@@

# File paths
game_stats_path <- "~/nfl/data/analysis_data/game_stats/merged_player_game.parquet"
mahomes_predictions_path <- "~/nfl/data/analysis_data/mahomes_lifetime_predictions.csv"

>>>>

---
title: "Defining Greatness"
subtitle: "A Comparative Analysis of Tom Brady and Patrick Mahomes"
author: 
  - Alexander Guarasci
thanks: "Code and data are available at: https://github.com/AlexanderG123/nfl"
date: today
date-format: long
abstract: "This paper compares NFL quarterbacks Tom Brady and Patrick Mahomes, focusing on their statistical performances. Analyzing their respective career data, this paper uses predictive modelling to forecast Patrick Mahomes future. It finds that while both have impressive career statistics, ultimately, playoff victories, particularly Super Bowl wins, serve as a more definitive measure of greatness. By examining these players, the paper highlights how the NFL’s dynamic context impacts player evaluation and legacy assessment."
format: 
  pdf: 
    fig-pos: "H"
number-sections: false
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

The analysis was conducted in R [@citeR], leveraging tools from the Tidyverse [@citetidyverse], Arrow [@citearrow], Knitr [@citeknitr], Testthat [@citett] packages. The primary dataset included QB-specific data from every NFL game played since 2000, encompassing over 55 columns detailing various player performance metrics. Additional data sources were used for advanced metrics, notably ESPN’s Quarterback Rating (QBR), which encapsulates QB efficiency across multiple dimensions of gameplay.

@@

# File paths
game_stats_path <- "~/nfl/data/analysis_data/game_stats/merged_player_game.parquet"
mahomes_predictions_path <- "~/nfl/data/model_data/mahomes_lifetime_predictions.csv"
